A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-16 main.tex
Turnitin done

Findings suggest that mindfulness-breathing-stretching interventions appear to offer potential improvement or stabilization of neuroendocrine-immune activity in breast cancer survivors compared to control groups.
This review revealed a positive pattern between spiritually-based interventions and several PNI biomarker outcomes, suggesting that spiritually-based interventions offer positive mental and physiological health benefits. For breast cancer survivors, these studies suggested that engaging in spiritually-based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.

@@

In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo. If I had thought of any internal medicine, it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}.
Cullen studied the objective science of analytical chemistry. He also sensed that the patient's subjective, psychosomatic, or "sympathetic constitution" determined his reaction to a prescribed therapeutic substance.
Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with the psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
Cullen's theory of sympathy is a mind-body function, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.

@@

Cullen's lecture notes reveal a sophisticated clinical understanding of mind-body interaction centred on a physician's therapeutic intentions to patient sympathy\cite{Sapin2014}.

@@

The physician's role was to be a gentle, sympathetic listener who could interpret the patient's sympathetic disorder and select the proper remedy to treat it, either by prescribing placebos to please (influence the patients' emotional states) medicine to cure the patient's disorder.

>>>>

Findings suggest that mindfulness meditation could stabilize neuroendocrine-immune activity (measured by PNI biomarkers) in breast cancer patients comparing to control groups\cite{Hulett2016}.
%This review revealed a positive pattern between spiritually-based interventions and several PNI biomarker outcomes, suggesting that spiritually-based interventions offer positive mental and physiological health benefits. 
%For breast cancer survivors, these studies suggested that engaging in spiritually-based practices may improve or stabilize the immune profile dysregulation that occurs with breast cancer.\cite{Hulett2016}.

@@

In 1772, Willian Cullen, a British physician, wrote that  "I own that I did not trust much to it, but I gave it because it is necessary to give a medicine, and as what I call a placebo. If I had thought of any internal medicine, it would have been a dose of the Dover's powders (made up of Ipecac and opium)."\cite{Kerr2008}\cite{Finniss2018}
Cullen studied the objective science of analytical chemistry. He also studied that the patient's therapeutic response could be influenced by his
subjective, psychosomatic, or "sympathetic constitution"\cite{Kerr2008}.
%Cullen developed a theory of "sympathy" (or empathy) which informed his ideas about clinical medicine dealing with the psychosomatic theory of illness and mind-body therapeutics. % he do 炮製
Cullen's theory of sympathy (or empathy) is a mind-body therapeutics, a kind of "vital force" that animated the human body, joint function, and transmitted sensation to target organs\cite{Forget2003}\cite{Kerr2008}.

@@

%Cullen found the power of mind-body interaction that a physician's therapeutic intentions could be triggered by sympathy\cite{Sapin2014}.

@@

The physician could listen and interpret the patient's sympathetic disorder and select either placebos to please (influence the patients' emotional states) or medicine to cure the patient's disorder.
